### 2014-02-28 thesis/src/abstract.tex
Thesis: abstract, impact

Cloud computing has become an attractive model for provisioning on demand computing resources as services to end-users. It is based on the assumption that almost anything can be viewed as a service, starting from applications delivered over Internet, through hardware in the data centers and ending on computing power. That model appears to be so attractive as from the user point of view the offered resources are infinite, transparent, robust and ready to consume at any time.

Most of the times end-users do not know in advance what the demand for the service is. This creates a requirement in which their systems are auto-scalable, i.e. they support sudden spikes in demand followed by underutilization at other times. An architecture of a cloud computing system, that meets these requirements, has a characteristic of a multi-hierarchical autonomic system, where different layers corresponds to different levels where cloud operates: starting from an application layer, through the application platform, infrastructure to end on a cloud instance.

Problem complexity raises challenges in a variety of aspects, especially in terms of providing cooperation and mutual sharing of resources that may belong to different kind of cloud providers. Therefore, an architecture that enables seamless cooperation among cloud providers and takes into account various QoS requirements of end-users be developed is absolutely vital. The InterCloud architecture is one of the first attempts that had been made in this direction. Having characteristic of an application platform in mind, we propose a variation of that architecture that supports cooperation among these application platform and fulfils needs of a decentralized environment.

>>>>

Cloud computing has become an attractive model for on demand provisioning of computing resources as services to end-users. It is based on the assumption that almost anything can be viewed as a service, starting from applications delivered over Internet, through hardware in the data centers and ending on computing power. That model appears to be so attractive as from the user point of view the offered resources are infinite, transparent, robust and ready to consume at any time.

Most of the times end-users do not know in advance what the demand for the service is. This creates a requirement in which their systems are auto-scalable, i.e. they support sudden spikes in demand followed by underutilization at other times. An architecture of a cloud computing system, that meets these requirements, has a characteristic of a multi-layered self-adaptive system, where different layers corresponds to different levels where cloud operates: starting from an application layer, through the application platform, infrastructure to end on a cloud instance.

Problem complexity raises challenges in a variety of aspects, especially in terms of providing cooperation and mutual sharing of resources that may belong to different cloud providers. Therefore, an architecture that enables seamless cooperation among cloud providers and takes into account various QoS requirements of end-users is absolutely vital. The InterCloud architecture is one of the first attempts that had been made in this direction. Having characteristic of an application platform in mind, we propose a variation of that architecture.

### 2014-02-28 thesis/src/chapters/chapter-introduction.tex
Thesis: abstract, impact

Having customer requirements in mind, it is crucial that a service provider is able to adapt itself to fulfil customer's contract. For example, such adaptation can be triggered by a sudden spike in resource demand and may result in provisioning additional application platforms. However, due to the problem complexity and number of concerns involved, there are different levels where adaptation is possible:
\begin{itemize}
	\item user application
	\item application platform
	\item infrastructure
\end{itemize}
What is more, the fact that single service provider is constrained by his finite amount of resources poses a risk that it may not be able to serve customer all the time. Consequently, it is expected that adaptation at a service provider level is also possible, i.e. provider can offload some traffic to a different provider, as long as it satisfies a customer.

@@

\section{Contributions}
The main contributions of this dissertation are as follows:
\begin{itemize}
  \item A proposal of an architecture of federated cloud computing environment, which is based on and can be viewed as a simplified version of \emph{InterCloud}
  \item The notion of considering each service model as an autonomic system
  \item The implementation of the proposed architecture using OpenNebula technology stack
  \item The evaluation of implemented proof-of-concept
\end{itemize}

\section{Impact}
We hope that the concept of representing each level of an autoscaling subsystem as an autonomic one can be thought-provoking for cloud computing scientists.  What is more, we believe that our successful attempt to implement a simplified variant of an InterCloud architecture will cause its gain in interest and popularity. 
Finally, we consider the ideas contained in this work be beneficial to the OpenNebula ecosystem as they provide insights into the ways Quality of Service can be ensured:
\begin{itemize}
  \item implementing autoscaling capabilities
  \item designing \emph{cloud infrastructure} in accordance with InterCloud architecture
\end{itemize}

>>>>

Having customer requirements in mind, it is crucial that a service provider is able to adapt itself to fulfil customer's contract. For example, such adaptation can be triggered by a sudden spike in resource demand and may result in provisioning additional application platforms. However, due to the problem complexity and number of concerns involved, there are different levels where adaptation is possible:
\begin{itemize}
	\item user application
	\item application platform
	\item infrastructure
\end{itemize}
What is more, the fact that a single service provider is constrained by his finite amount of resources poses a risk that it may not be able to serve customer all the time. Consequently, it is expected that adaptation at a service provider level is also possible, i.e. provider can offload some traffic to a different provider, as long as it satisfies a customer.

@@

\section{Contributions}
The main contributions of this dissertation are as follows:
\begin{itemize}
  \item A proposal of an architecture of a cloud computing federation, which is based on and can be viewed as a simplified version of \emph{InterCloud}
  \item The implementation of the proposed architecture using OpenNebula technology stack
  \item The evaluation of implemented proof-of-concept
\end{itemize}

\section{Impact}
We hope that the concept of self-adaptation at each level of cloud can be thought-provoking for computing scientists.  What is more, we believe that our successful attempt to implement a simplified variant of an InterCloud architecture will cause its gain in interest and popularity. 
Finally, we consider the ideas contained in this work be beneficial to the OpenNebula ecosystem as they provide insights into the ways Quality of Service can be assured:
\begin{itemize}
  \item implementing auto-scaling capabilities
  \item designing \emph{cloud infrastructure} in accordance with InterCloud architecture
\end{itemize}
